---
title: "Print Cat"
output:
  md_document:
     variant: markdown_github
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Cat and Print
## Print
A simple message
```{r}
print("Hello")
```

Now let's personalize it
```{r, error = TRUE}
name = "Josh"
print("Hello, my name is", name)
```

Hmm, why didn't that work?
```{r}
help(print)
```

Beacuse `print` needs everything that you want printed as the first argument.  We can do that with `paste`!

```{r}
name = "Josh"
print(paste("Hello, my name is", name))
```

Let's output some more information.  To make it easy to read let's put it on a new line by printing the _newline_ character `\n`.

```{r}
name = "Josh"
print(paste("Hello, my name is", name, ". \nToday we are learning some awesome R."))
```

That didn't work right. And also there is a space between "Josh" and the period, that's ugly.
We can fix all that . . .

```{r}
name = "Josh"
print(paste("Hello, my name is ", name, ".", sep=""))
print("Today we are learning some awesome R.")
```
. . . but it is starting to make our code more complicated.  And the "[1]" at the beginning of each line is kind of ugly.  Maybe it is time for a more powerful tool . . .

## Cat
`cat` is similar to `print`, but different.  It is more of a power tool, it gives you more control, but with that control comes a bit more work on your part.
```{r}
cat("Hello")
```

```{r}
name = "Josh"
cat("Hello, my name is", name)
```

```{r}
name = "Josh"
cat("Hello, my name is", name, ". \nToday we are learning some awesome R.")
```

## Print vs Cat
So why use `print` at all?  For a lot of day to day stuff it is more convenient.
```{r}
print("Hello! Let's do some math.")
1+1
print("That should equal 2")
```

```{r}
cat("Hello! Let's do some math.")
1+1
cat("That should equal 2")
```

All along `print` has been quietly putting a newline at the end of whatever it prints, that is _usually_ what we want.  `cat` doesn't do that automatically.  More _control_ also usually means more _work_ because control is usually the opposite of automatic.

We can get `cat` to do what we want, its just a bit more work:

```{r}
cat("Hello! Let's do some math.", fill=TRUE)
1+1
cat("That should equal 2")
```
 
 Of course more control also means more options . . .

```{r}
cat("Hello! Let's do some math.\n", 1+1, "\nThat should equal 2", fill=TRUE)
```

 