---
title: 'Bash and R: Shell Variables in RMarkdown'
output:
  md_document:
     variant: markdown_github
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Every R Chunk is a Piece of the Continent
As we have seen, R chunks share an environment - a variable defined in one R chunk is available in all the R chunks after it in the document.

```{r}
secret_identity="Dracula"
print(secret_identity)
```

```{r}
print(secret_identity)
```

```{r}
secret_identity="Count Chocula"
print(secret_identity)
```

```{r}
print(secret_identity)
```

# Every Bash Chunk is an Island
In RMarkdown bash chunks behave differently than R chunks. In RMarkdown each bash chunk is its own environment, so shell variables defined in one bash chunk are not available in any others.

```{bash}
export SECRET_IDENTITY=Dracula
echo $SECRET_IDENTITY
```

```{bash}
echo $SECRET_IDENTITY
```
> By default bash does not raise an error when you try to use an undefined variable, undefined variables just default to empty values.  

```{bash error=TRUE}
set -u
echo $SECRET_IDENTITY
```
> `set -u` is a safety belt - after calling it in a bash session, bash *will* raise an error if you try to use an undefined variable. Of course, in Rmarkdown calling `set -u` in a chunk only affects that chunk.


# Building an R Bridge to Bash
R can communicate with bash through shell variables.  We can define shell variables using the R function `Sys.setenv`.
```{r}
Sys.setenv(MY_NAME="Inigo Montoya")
```

The bash chunks in an RMarkdown document borrow the environment of the R chunks, so shell variables defined with `Sys.setenv` are available within bash chunks.

```{bash}
echo $MY_NAME
```

R chunks can get the values of shell variables with `Sys.getenv`, although it doesn't work for shell variables defined within a bash chunk

```{r}
Sys.getenv("MY_NAME")
```

`Sys.setenv` can assign a value to a shell variable from an R variable
```{r}
Sys.setenv(SECRET_IDENTITY=secret_identity)
```

```{bash}
echo $SECRET_IDENTITY
```


There is no need for the shell variable to have the same name as the R variable.
```{r}
Sys.setenv(MY_NAME=secret_identity)
```

```{bash}
echo $MY_NAME
```

It is common practice for the names of shell variables to be capitalized, but that is not a requirment
```{r}
Sys.setenv(icecream="Cookie Dough")
```

```{bash}
echo $icecream
```


