---
title: "Diversity Measures"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(vegan)
library(tibble)
```

default is to use natural logarithms. Shannon index
is calculated with:
> H <- diversity(BCI)

which finds diversity indices for all sites.
Vegan does not have indices for evenness (equitability), but the most common of these, Pielou’s
evenness J = H0/ log(S) is easily found as:

> J <- H/log(specnumber(BCI))

```{r}
evenness = function(x){
  J <- diversity(x)/log(specnumber(x))
  return(J)
}
```

# Calculations for diversity lecture slides
```{r}
tribble(
  ~group, ~red, ~yellow, ~blue, ~white, ~green,
  "a",   5,   5,   5,   5,   5,
  "b",   16,  1,   1,   1,   1,
  "c",   20,  0,   0,   0,   0
  ) %>%
  column_to_rownames("group") ->
  star_data

specnumber(star_data)
diversity(star_data)
evenness(star_data)

diversity(star_data*10)
evenness(star_data*10)

```

```{r}
tribble(
  ~group, ~red, ~yellow, ~blue, ~white, ~green, ~pink, ~orange, ~black, ~purple, ~lime,
  "a",   5,   5,   5,   5,   5,   0,   0,   0,   0,   0,
  "b",   5,   5,   5,   5,   5,   5,   5,   5,   5,   5,
  "c",   16,  1,   1,   1,   1,   1,   1,   1,   1,   1,
  "d",   16,  1,   1,   1,   1,   0,   0,   0,   0,   0,
  "e",   20,  0,   0,   0,   0,   0,   0,   0,   0,   0
  ) %>%
  column_to_rownames("group") ->
  star_data

tibble(richness = specnumber(star_data),
       shannon = diversity(star_data), 
       evenness = evenness(star_data))
```

```{r}
tribble(
  ~group, ~red, ~yellow, ~blue, ~white, ~green, ~pink, ~orange, ~black, ~purple, ~lime,
  "a",   5,   5,   5,   5,   5,   0,   0,   0,   0,   0,
  "b",   5,   5,   5,   5,   5,   5,   5,   5,   5,   5,
  "d",   16,  1,   1,   1,   1,   0,   0,   0,   0,   0
  ) %>%
  column_to_rownames("group") ->
  star_data

tibble(richness = specnumber(star_data),
       shannon = diversity(star_data), 
       simpson = diversity(star_data, index="simpson"), 
       evenness = evenness(star_data),
       chao1 = estimateR(star_data)["S.chao1",],
       ace = estimateR(star_data)["S.ACE",]
       ) %>% 
  t
```

```{r}
estimateR(star_data)["S.chao1",] 
```

```{r}

tribble(
  ~color, ~Jar1,	~Jar2, ~Jar3, ~Jar4,
  "Red", 8, 5, 2, 1,
  "Yellow", 0, 1, 2, 2,
  "Green", 0, 1, 2, 2,
  "Blue", 0, 1, 2, 3) %>%
  column_to_rownames("color") %>%
  t ->
  jar_data
jar_data
```

```{r}
tibble(richness = specnumber(jar_data),
       shannon = diversity(jar_data), 
       simpson = diversity(jar_data, index="simpson"), 
      ) %>%
  t
```
