---
title: "IBIEM Computing"
output:
  md_document:
    variant: markdown_github
  html_document: default
---

The IBIEM bootcamp and the CSP1 and CSP2 courses depend heavily on computing so please read this information carefully.  This document is also available at https://github.com/ibiem-2020/ibiem_2020_material/tree/master/content/misc/bootcamp_email.md


# Computer
Many bootcamp sessions and CSP1 and CSP2 class will involve computer work, so you *must* have a computing device available. You do not need a brand-new, super-fast computer. As discussed below, all of our computational work will be in a web-browser based environment, so you just need to be able to run an up-to-date web browser. You *may* be able to get away with a tablet. If you do not have access to a computing device please contact us as soon as possible so we can make arrangements for a loaner computer.


# IBIEM computing environment
All computational work for the IBIEM will be done through a web browser-based version of RStudio.  Our RStudio instances are being run by the Duke Office of Information Technology, so all you need on your computer is an up-to-date version of Firefox, Chrome, or Safari.  



## Accessing the IBIEM computing environment
### Non-Duke Students
You can try the instructions below, but the "VM-Manage" system does not usually work with guest NetIDs. You should have already received an email from me with instructions on how to access your RStudio instance

### Duke Students

To access your RStudio instance:

1. Go to https://vm-manage.oit.duke.edu/
2. Logon with your NetID and Password
3. Click on "Docker" in the top right.
4. You should see a link that says "Click here to log in to your IBIEM2020 environment".  You should click on that link.
5. If you do not see this link, scroll down until you find the section “IBIEM2020 - RStudio for bootcamp, CSP1, and CSP2 2020" and Click on the link that says “Click here to create your personal IBIEM2020 environment”
   - Important: Be sure that you select IBIEM2020! There are versions of the IBIEM environment from previous years!  You do not want these!!

# IBIEM Login confirmation
In order to catch and fix any problems ahead of time, you *must* log into the IBIEM Computing Environment as soon as possible and confirm your successful login.  You will be recieving an email later today with a link for a "Login Confirmation" form.  To complete this process please do the following:

1. Follow the instructions above for logging into the IBIEM Computing Environment

2. Once RStudio is open in your web browser, type or paste the following command into the *Console* pane (on the left side of the RStudio window), then hit the *return* key on your keyboard: 

```{r eval=FALSE, echo=TRUE}
readLines("/data/confirm.md")
```

You should see the following output:
```
[1] "The login confirmation number is: #####"
```
where ##### is a 5 digit number.  

3. You will need to type or paste the 5 digit number into the "Login Confirmation" form and submit it.

4. Once you do that, you should receive a message "IBIEM Login Confirmed! Thank you!”

5. Next type or paste the following command into the *Console* pane , then hit the *return* key on your keyboard: 

```{r eval=FALSE, echo=TRUE}
readLines(path.expand("~/test_account.txt"))
```
You *should* get an error message that says `Error in file(con, "r") : cannot open the connection`. If you *do not* get this error message, please email me *immediately* to let me know

6. Finally you should type or paste the following command into the *Console* pane , then hit the *return* key on your keyboard: 

```{r eval=FALSE, echo=TRUE}
cat(file = path.expand("~/test_account.txt"), "Account accessed\n")
```
