---
title: "Download IBIEM 2020 Project Data From DDS"
output:
  md_document:
    variant: markdown_github
  html_document:
    toc: false
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  eval=FALSE)
```


# Setup ddsclient
1. Generate a DDS key following instruction from: <https://github.com/Duke-GCB/DukeDSClient/wiki/Agent-User-Keys-(setup)>
2. Open a new text file, paste in DDS key, and save as `~/.ddsclient`
3. Run the following chunk to set DDS key permissions

```{r}
project_data_dir="/data/project_data"
dir.create(project_data_dir)
Sys.setenv(PROJECT_DATA_DIR=project_data_dir)
```



```{bash}
# change permissions to make ddsclient happy
chmod 600 ~/.ddsclient
```

# Download Data
```{bash}
ddsclient -h
```

Figure out which project to download
```{bash}
ddsclient list
```

Check project contents
```{bash eval=FALSE, include=FALSE}
ddsclient list -p IBIEM_2020
```

Download data
```{bash}
ddsclient download -p IBIEM_2020 $PROJECT_DATA_DIR
```


```{bash}
df -hl
```


```{bash eval=FALSE, include=FALSE}
ddsclient list -p IBIEM_2019
```

Does -p IBIEM_2019 /argonne_data/ have data for both of these:
Project 1 - Microbiome adaptation to plastics
Project 2 - Using silicone bands to monitor personal microbiomes and chemical exposome


```{bash}
df -hl
```

```{bash}
ddsclient download -p IBIEM_2019 --include argonne_data $PROJECT_DATA_DIR

```

```{bash}
ddsclient download -h

```

```{bash}
df -hl
```


```{bash}
ddsclient download -p "GunschLab " \
  --include McCumber/Pig_lungs/ \
  $PROJECT_DATA_DIR
```

```{bash}
df -hl
```

```{bash}
ls $PROJECT_DATA_DIR/McCumber/Pig_lungs/Data/Reads_Fungal
```

```{bash}
cd $PROJECT_DATA_DIR/McCumber/Pig_lungs/Data/Reads_Fungal
md5sum -c md5_checksum_uncompressed_fastqs.txt

gzip *.fastq
md5sum *.fastq.gz > md5_checksum.txt
```







Set data directory read only
```{bash eval=FALSE, include=FALSE}
chmod -R a-w /data/tutorial_data/IBIEM_2016
```

